\vspace{5em}On Evaluating Adversarial Robustness

### 2019-02-20 paper.tex
Fix typo and minor grammar changes

  Nicholas Carlini\textsuperscript{1},
  Anish Athalye\textsuperscript{2},
  Nicolas Papernot\textsuperscript{1},
  Wieland Brendel\textsuperscript{3},
  Jonas Rauber\textsuperscript{3},
  Dimitris Tsipras\textsuperscript{2},
  Ian Goodfellow\textsuperscript{1},
  Aleksander M\k{a}dry\textsuperscript{2}
  \\
  \noindent \\
  \noindent \\
  \textsuperscript{1} Google Brain
  \textsuperscript{2} MIT 
  \textsuperscript{3} University of T\"ubingen

>>>>

  Nicholas Carlini\textsuperscript{1},
  Anish Athalye\textsuperscript{2},
  Nicolas Papernot\textsuperscript{1},
  Wieland Brendel\textsuperscript{3},
  Jonas Rauber\textsuperscript{3},
  Dimitris Tsipras\textsuperscript{2},
  Ian Goodfellow\textsuperscript{1},
  Aleksander M\k{a}dry\textsuperscript{2},
  Alexey Kurakin\textsuperscript{1}\,\textsuperscript{*}
  \\
  \noindent \\
  \noindent \\
  \textsuperscript{1} Google Brain
  \textsuperscript{2} MIT 
  \textsuperscript{3} University of T\"ubingen
  \\
  \noindent \\
  \noindent \\
  \textsuperscript{*} List of authors is dynamic and subject to change.
  Authors are ordered according to the amount of their contribution
  to the text of the paper.
